\documentclass{article}
\usepackage{cite}
\usepackage{array}

\title{\textbf{AVSpeech Data Filtering}}
\author{Ami Baid}
\date{May 2023}

\begin{document}
\maketitle

\begin{flushleft}
    \large
    The AVSpeech dataset \cite{DBLP:journals/corr/abs-1804-03619} consists of 3-10 second clips from 290k YouTube videos, most of which feature a single speaker and little background noise. We utilize a subset of the AVSpeech dataset, filtering out videos that are not well-suited for visual acoustic matching—i.e., videos that have little audio-visual correspondence. To filter the dataset, we use the Vision-and-Language Transformer model (ViLT) fine-tuned on VQAv2 \cite{kim2021vilt}. Given an image-question pair, the ViLT model performs a classification task with 3,129 different answer classes, where each class corresponds to a natural language word. \\
    We observe that the model accurately answered a variety of yes-or-no questions about the visible setting in each clip. Since the clips are primarily recorded using a static camera, we ran the model for inference using a representative frame from each video. For each question, we selected a confidence threshold that filtered out clips likely to have the corresponding failure modes based on prior manual inspection. \\
    Videos deemed to have low audio-visual correspondence (e.g., images where the speaker is using a microphone, images with a virtual background) were removed from the training set. The initial set of 123,841 video clips is reduced by 38\%, resulting in 76,473 video clips with high audio-visual correspondence that were used for training. See Supp. for the specific questions and confidence thresholds used. 
\end{flushleft}

\pagebreak

\begin{center}
\begin{table}
\centering
\caption{\textbf{Questions and thresholds used for filtering AVSpeech data}}
\begin{tabular}{m{6.5cm}|m{2cm}|m{2cm}} 
    \hline
    Question & Answer & Threshold\\
    \hline
    Is a microphone or headset visible in the image & yes & 0.35\\
    \hline
    Is there a whiteboard/blackboard in the background & yes & 0.993\\
    \hline
    Is the entire background one solid color and material? & yes & 0.995\\
    \hline
    Is there a large projector screen covering most of the background? & yes & 0.999\\
    \hline
    Is part or all of the background virtual? & yes & 0.6\\
    \hline
    Are there multiple screens in the image? & yes & 0.995\\
    \hline
    Is the wider room clearly visible? & no & 0.985\\
    \hline
\end{tabular}
\end{table}
\end{center}

\pagebreak
\bibliography{references}
\bibliographystyle{plain}

\end{document}
